The globular cluster system of the Auriga simulations

### 2020-04-06 response_to_referee.tex

\documentclass{article}

\begin{document}

\section*{Introduction (of referee report)}
We thank the referee for a thoughtful and elaborate report that we feel greatly
improved the manuscript. We address the comments in sections with names that match
the headings of the referee report, starting with the following listing of our 
response to the 3 paragraphs in the introduction.
\begin{enumerate}
\item We updated the abstract and conclusion to clarify that we meant to describe
what would be needed for the environmental dependence of the formation and disruption
of bound clusters for the Auriga simulations to be consistent with the observations,
rather than to argue that the Auriga simulations reflect these trends.
\item
We feel that our conclusion would be too strongly phrased if we would generalise 
our results obtained using the Auriga simulations to cosmological simulations 
in general. We find that age-selected stellar particles in the Auriga simulations 
do not reproduce key properties of observed GC systems in the Milky Way and M31.
However, our results might reflect characteristics that are specific to Auriga, 
e.g. that the galaxy formation model overmixes metals at early times. 
Therefore we did add a final bulletpoint to our conclusion to clarify the above, 
but we limit the scope to the Auriga simulations. Thanks for pointing this out!

Furthermore, we clarified in the manuscript that we investigate the metallicity
and galactocentric radius because these properties are available for the observed
GC systems and in the simulations.
\end{enumerate}

### 2020-04-06 AurigaGCS.tex
First removal of parenthesis to improve readability

We show the mean metallicity and standard deviation of all $30$~Auriga L4 haloes
in Figure~\ref{fig:FeH_mu_sigma} to illustrate the behaviour for the full set of Auriga
galaxies. The beige crosses are to be compared to the purple (magenta) cross, 
which shows the mean value of all MW (M31) GCs. In addition, we show the metal-rich 
(metal-poor) population of the MW GCS using a solid (open) dot. We caution that
these literature values result from individual Gaussian fits to sub sets of the 
observational data cut at [Fe/H]~$= -1$. We do not include corresponding data 
points calculated using such an artificial cut for the simulated star particles.
It is interesting that the mean metallicities of the {\it in~situ} GC candidates 
appear roughly consistent with that of the metal-rich population of the MW despite 
the lack of such a metallicity cut, although the simulations show larger dispersions. 
The latter could simply be caused by the hard separation of the MW data into two 
groups, which means the range is smaller and the resulting dispersion lower. With 
regard to the M31 GCS, so far no definitive consensus has been reached
in the literature concerning uni- bi- or trimodality in the [Fe/H] distribution, 
but CR16 argues that the data, after removal of younger objects due to improved 
age classification, hints at three populations separated at [Fe/H]~$=-0.4$ and 
[Fe/H]~$ = 1.5$. None of the Auriga sub sets has a mean value that offers much 
hope that the simulated distribution is consistent with the lowest metallicity 
group in the M31 GCS. This is also true for the metal-poor population of the 
MW with a mean value of $-1.6$. The main result of this figure is 
that all Auriga L4 galaxies have metallicity distributions with (much) larger
mean values than what is observed for the MW and M31 GCS, and that we 
systematically find lower mean metallicities for the accreted GC candidates
than for those that have formed {\it in~situ}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        L4 simulations. We show the median value of all Auriga haloes for all
        stars (beige dotted) and GC candidates (i.e. stars with
        age $>$~10~Gyr; beige solid). The latter sub set is further split up
        between stars that formed {\it in~situ} (brown solid), and those that were accreted
        (teal solid). Shaded regions indicate the 25-75 percentile range. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the second goal, which is to see whether sufficient total mass in 
GC candidates is produced by the Auriga simulations. To answer this question we plot
a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
median for all $30$~Auriga L4 haloes and the 25-75 percentile range 
(shaded regions, which shows the scatter between runs that have different initial 
conditions, thus, have unique merger histories). We chose to aggregate the data 
to indicate general trends that we find when the GC candidates are split up into
the accreted and {\it in situ} subsets, rather than selecting typical examples 
of individual (simulated) galaxies. Once again we notice that the peak metallicity 
shifts down from [Fe/H]~=~$0$ to [Fe/H]~=~$-0.6$ for GC candidates compared to all stars, 
and we find that the mass at the peak lowers by roughly one dex. The mass budget 
of the GC candidates is dominated by the {\it in~situ} subpopulation above
[Fe/H]~=~$-1$, and by the accreted subset below this value. We show the MW (M31) 
GCS in purple (magenta) and notice that the difference between the MW and M31 
distributions is substantially larger than the scatter between different Auriga 
galaxies, particularly around [Fe/H]~$=-1$. In addition, M31 does host 
(a handful of) GCs with [Fe/H]~$< -2.5$ as well as GCs with [Fe/H]~$ > 0$ while 
the MW does not.

>>>>

We show the mean metallicity and standard deviation of all $30$~Auriga L4 haloes
in Figure~\ref{fig:FeH_mu_sigma} to illustrate the behaviour for the full set of Auriga
galaxies. The beige crosses are to be compared to the purple and magenta cross, 
which shows the mean value of all MW and M31 GCs, respectively. In addition, we 
show the metal-rich population of the MW GCS using a solid dot, and the metal-poor
population with an open dot. We caution that
these literature values result from individual Gaussian fits to sub sets of the 
observational data cut at [Fe/H]~$= -1$. We do not include corresponding data 
points calculated using such an artificial cut for the simulated star particles.
It is interesting that the mean metallicities of the {\it in~situ} GC candidates 
appear roughly consistent with that of the metal-rich population of the MW despite 
the lack of such a metallicity cut, although the simulations show larger dispersions. 
The latter could simply be caused by the hard separation of the MW data into two 
groups, which means the range is smaller and the resulting dispersion lower. With 
regard to the M31 GCS, so far no definitive consensus has been reached
in the literature concerning uni- bi- or trimodality in the [Fe/H] distribution, 
but CR16 argues that the data, after removal of younger objects due to improved 
age classification, hints at three populations separated at [Fe/H]~$=-0.4$ and 
[Fe/H]~$ = 1.5$. None of the Auriga sub sets has a mean value that offers much 
hope that the simulated distribution is consistent with the lowest metallicity 
group in the M31 GCS. This is also true for the metal-poor population of the 
MW with a mean value of $-1.6$. The main result of this figure is 
that all Auriga L4 galaxies have metallicity distributions with (much) larger
mean values than what is observed for the MW and M31 GCS, and that we 
systematically find lower mean metallicities for the accreted GC candidates
than for those that have formed {\it in~situ}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        L4 simulations. We show the median value of all Auriga haloes for all
        stars (beige dotted) and GC candidates (i.e. stars with
        age $>$~10~Gyr; beige solid). The latter sub set is further split up
        between stars that formed {\it in~situ} (brown solid), and those that were accreted
        (teal solid). Shaded regions indicate the 25-75 percentile range. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the second goal, which is to see whether sufficient total mass in 
GC candidates is produced by the Auriga simulations. To answer this question we plot
a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
median for all $30$~Auriga L4 haloes and the 25-75 percentile range 
(shaded regions, which shows the scatter between runs that have different initial 
conditions, thus, have unique merger histories). We chose to aggregate the data 
to indicate general trends that we find when the GC candidates are split up into
the accreted and {\it in situ} subsets, rather than selecting typical examples 
of individual (simulated) galaxies. Once again we notice that the peak metallicity 
shifts down from [Fe/H]~=~$0$ to [Fe/H]~=~$-0.6$ for GC candidates compared to all stars, 
and we find that the mass at the peak lowers by roughly one dex. The mass budget 
of the GC candidates is dominated by the {\it in~situ} subpopulation above
[Fe/H]~=~$-1$, and by the accreted subset below this value. We show the MW GCS 
in purple and that of M31 in magenta, and notice that the difference between the 
MW and M31 distributions is substantially larger than the scatter between different 
Auriga galaxies, particularly around [Fe/H]~$=-1$. In addition, M31 does host 
(a handful of) GCs with [Fe/H]~$< -2.5$ as well as GCs with [Fe/H]~$ > 0$ while 
the MW does not.
